Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-17 paper.tex
update

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major challenges faced by researchers, semantic matchmaking and Quality of Service (QoS) optimisation. Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning. QoS optimisation aims to optimise the non-functional requirements of service users, e.g., minimum cost, maximal reliability. Many scholars have looked into QoS optimisation problems in QoS-aware web service composition, applying AI planning and Evolutionary Computation techniques. To meet users' requirements, one often needs to consider both semantic matchmaking quality and QoS simultaneously. Existing works on web service composition often concern either semantic web  service composition or QoS-aware web service composition. However, there are few works concerning both semantic matchmaking quality and QoS at the same time and achieving a more desirable tradeoff in consideration of both sides. Therefore, we propose a general comprehensive quality model considering semantic matchmaking quality and QoS in this paper. This model is also suitable to be tackled through EC algorithms. Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model. This method can generate a more desirable balance in considering semantic matchmaking quality and QoS requirements that is supported by our experiment when compared to QoS-aware approach. We also conduct another experiment that shows our PSO-based method performs better in finding a more optimised solution by comparing with one existing GP-based method.

@@

\section{Related Work} \label{relatedWork}
Substantial work on web service composition focused on either semantic web service composition \cite{boustil2014semantic,mier2015integrated,bansal2016generalized} or QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,gupta2015optimization,qi2010combining,ma2015hybrid}, However few researchers addressed both semantic matchmaking quality and QoS requirements at the same time for web service composition problems. To the best of our knowledge, \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} reported some recent attempts on service composition that considers both aspects.

\cite{boustil2014semantic,mier2015integrated,bansal2016generalized} captures the semantics of web services' parameters using some kind of logic (e.g., description logic) for enabling semantic web service composition, where the number of web services or length of the graph is minimised to reach the optimised graph-based composition solutions. However, these approaches need to be improved for the scalability that considering a large number of web services, and the evaluation method does not fit properly for customers' complex requirements.

>>>>

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major challenges faced by researchers, semantic matchmaking and Quality of Service (QoS) optimisation. Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning. QoS optimisation aims to optimise the non-functional requirements of service users, e.g., minimum cost, maximal reliability. Many scholars have looked into QoS optimisation problems in QoS-aware web service composition, applying AI planning and Evolutionary Computation techniques. To meet users' requirements, one often needs to consider both semantic matchmaking quality and QoS simultaneously. Existing works on web service composition often concern either semantic web  service composition or QoS-aware web service composition. Therefore, we propose a general comprehensive quality model considering semantic matchmaking quality and QoS simultaneously that can achieve a more desirable trade-off in consideration of both sides by conducting an experiment comparing with promising QoS-aware model. Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model, and compare the PSO-based method with one recent GP-based method to show its performance in finding a more optimised solution.

@@

\section{Related Work} \label{relatedWork}
Substantial work on web service composition focused on either semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive}, However few researchers addressed both semantic matchmaking quality and QoS requirements at the same time for web service composition problems. To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some recent attempts on service composition that considers both aspects.

\cite{boustil2014semantic,bansal2016generalized,mier2015integrated} captures the semantics of web services' parameters using some kind of logic (e.g., description logic) for enabling semantic web service composition, where the number of web services or length of the graph is minimised to reach the optimised graph-based composition solutions. However, these approaches need to be improved for the scalability that considering a large number of web services, and the evaluation method does not fit properly for customers' complex requirements.
